---
title: "Urban Areas Whose Names Start With The Letter R"
author: "Agelink"
date: "June, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Demonstration of the leaflet R package

Made for a course assignment. Below R code generates the shown map with markers
for populated urban areas whose name starts with R. 
The reason I say urban areas
is that the dataset, despite being named "cities", also gave me "Retiro" which
I happen to know is a neigbourhood (barrio) of Madrid City, not a city in its
own right.

```{r}
fileurl<-"http://download.geonames.org/export/dump/cities15000.zip"
download.file(fileurl,destfile="cities.zip",method="auto")
connection<-unz("cities.zip",filename="cities15000.txt")
cities<-read.csv(connection,sep="\t",header=F)
cities<-cities[grep("^R",cities$V3),]
library(leaflet)
map<-addTiles(leaflet())
map<-addMarkers(map,lng=cities$V6,lat=cities$V5,popup=cities$V3,
		clusterOptions=markerClusterOptions())
map
```

Credit to geonames.org for being kind enough to make their data available
under the CC Attribution 4.0 International (CC BY 4.0) license.
(https://creativecommons.org/licenses/by/4.0/)

Also all credit to the creators and maintainers of R and its packages who
make it possible to, with just the few commands noted above, create
demonstration pages like this one.

The leaflet software itself displays the intellectual property rights associated
with the the map data it uses: it should be visible in the map above.

```{r}
date()
sessionInfo()
```
